\chapter{Introduction}
\label{chapter1}

Climate change calls for a shift to renewable energy and restructuring of the electricity sector.
Sources \cite{eurostat2020} show as of the time of reading this paper, 44 \% of produced electricity in Europe was from combustible sources such as gas, fuel, and coal. Even 
though that is a significant decrease of 10 \% in the last 10 years, it is a significant Co2 emitter.
The same source \cite{eurostat2020} also states that a third of energy is consumed by the residential sector. It is estimated, 
that the human population will reach 10 billion inhabitants in the next 10 years, and ever-increasing ownership of electrical appliances such as smartphones, HVACs, and EVs will further increase energy consumption. (elevate this issue)
Acknowledging that, reducing consumption in that sector could leave a significant impact on the human footprint. 

%increased time spent indoors*

The EU aims to be climate neutral by 2050, therefore it seeks to improve the efficiency of every part of pollution contributors through The European Green Deal.
A large part of these contributors is the Energy sector.
A subpart of the energy sector is the residential sector, where many advancements could be made to help to reach the goal.  

This could be achieved through various applications and methods that use load profiling and load monitoring as their core technology.
Authors in \cite{Chuan2014} proposed a method to reduce peak loads by studying consumer
appliance usage patterns. Paper \cite{Csoknyai2019} studied consumer usage patterns, and returned feedback that contributed to reducing consumption.
Another notable way is the use of distributed energy resources and managing them in such a way as to decrease the net output of energy flow such as the authors describe in
\cite{MORENOJARAMILLO2021445}. All described methods would reduce and alleviate the load off the power grid.

%can lead to improving their user behavior. 

Load profiling in building energy consumption is not a novelty and had been in research since the 1980s.
While it was thought that aggregated load profiles of households are relatively predictable, recent data obtained using smart meter data showed large deviance from user to user due to different lifestyles, as the author states in \cite{Review2021}.
In recent years load profiles have changed due to renewable energy accelerated development of distributed energy resources such as residential photovoltaic
power plants, home wind energy, and using EVs and home batteries. Socioeconomic changes such as work-from-home, also drastically reshaped the load profile curve. 

% It has been proved that existing load profiles (universal) do a decent job at estimating daily usage of houses in general,
% but fail to model a good per-house profile, due to large deviance in user consumption as author stated in \cite{Proedrou2021}. 
% Shift towards self-generation, increasing possession of EVs and shifts in socioeconomic patterns (work-from home), do not help either.  

Technology advancements in non-intrusive load monitoring and increased adoption of smart energy meters offer a new
way of load profiling, that is NILM load profiling.


% \section{Structure and contributions}
% M.Sc. degree will be composed of the following parts. In the first part, I will define what is load profiling, appliance level load profiling, 
% non-intrusive load monitoring, intrusive load monitoring, and anomaly detection. Then I will review related research work done to date. Next, I will elaborate 
% on existing ideas on where load profiling is being used to date and what are its possible applications. Then, I will present used datasets, and finally,
% I will present a working demo using appliance classification and simple load profiling.
% The demo will present the possible use of one of the previously mentioned applications. 

% The rough outline of chapters: 
% \begin{outline}
% 	\1 Abstract?
% 	\1 Introduction
% 	\1 Define load profiling
% 	\1 Anomaly detection (how it fits in) maybe?
% 	\1 Related work
% 	\1 Define contributions and goals
% 	\1 Present "Demo"
% 	\1 Methodology
% 	\2 Datasets (used)
% 	\2 Load classification
% 	\3 Mention my work on images?
% 	\3 Machine learning
% 	\2 Load profiling method
% 	\1 Results
% 	\1 Use cases
% 	\1 Privacy
% 	\2 Concerns
% 	\2 Sharing and transparency
% 	\2 Solutions
% 	\1 Datasets
% 	\2 Issues 
% 	\2 Load profiling
% 	\2 Solutions
% 	\1 Future research directions
% 	\2 Map of current work
% 	\2 Where does NILM load profiling lay on the Map
% 	\1 Discussion
% 	\1 Conclusions
	
% 	\end{outline}