% Appendix A

\chapter{The Source Code, High-Resolution Figures and Datasets} % Main appendix title

\label{AppendixA} % For referencing this appendix elsewhere, use \ref{AppendixA}

The following appendix contains mostly links that point to GitHub.
GitHub should be a valid repository for such projects, where links should persist indefinitely.
In case the links do eventually break, you can find the repository of thesis and demos under the username "jenkoj", under "msc" and "appliance-profiling".

\section{The source code}

The source code used in this chapter can be found in a GitHub repository: \\
\noindent \url{https://github.com/jenkoj/appliance-profiling} \\

\noindent Individual scripts can be found in the following Jupyter Notebooks: \\

\noindent The source code for generating the figures can be found at: \\
\noindent \url{https://github.com/jenkoj/appliance-profiling/blob/main/profilng_slices.ipynb} \\

\noindent The source code for t-SNE can be found at: \\
\noindent \url{https://github.com/jenkoj/appliance-profiling/blob/main/t_SNE.ipynb} \\

\noindent the source code for elderly care can be found at: \\
\noindent \url{https://github.com/jenkoj/appliance-profiling/blob/main/elderly_care_demo.ipynb} \\

\section{High resolution figures}

\noindent High-resolution figures can be found in the thesis repository \url{https://github.com/jenkoj/msc}. \\
\noindent More precisely in the "figures" subfolder \url{https://github.com/jenkoj/msc/tree/main/Figures}. \\

\section{Data and datasets}

\noindent We cannot share the data since it is not ours to share, but we can share the spreadsheet that points to each dataset.
\noindent The spreadsheet includes other datasets that could be used for the very same purpose.
\noindent The spreadsheet can be found here.  \\

\noindent \url{https://github.com/jenkoj/msc/blob/main/Appendices/datasets_and_sources.pdf} \\

\noindent An overview of the data in the datasets was made, and it can be seen in the following spreadsheet.  \\
\noindent \url{https://github.com/jenkoj/msc/blob/main/Appendices/dataset_overview.pdf} \\

\noindent The sliced hourly datasets can be found here. \\
\noindent \url{https://drive.google.com/drive/folders/1tIsG-bqxoJdbU1p8xa_LCTaKNSk_LylZ?usp=sharing} \\




% {mall\verb!\hypersetup{urlcolor=red}!}, or

% {\small\verb!\hypersetup{citecolor=green}!}, or

% {\small\verb!\hypersetup{allcolor=blue}!}.

% \noindent If you want to completely hide the links, you can use: 

% {\small\verb!\hypersetup{allcolors=.}!}, or even better: 

% {\small\verb!\hypersetup{hidelinks}!}.

% \noindent If you want to have obvious links in the PDF but not the printed text, use:

% {\small\verb!\hypersetup{colorlinks=false}!}.
% \s